---
title: "Code"
author: "Lauren Abdallah"
date: "03/07/2021"
output:
  html_document:
    theme: lumen
    toc: true
  pdf_document: default
---

# Experiment 1
 
```{r}

#Loading relevant packages
library(tidyverse)
library(dplyr)
library(qualtRics)
library(tidyr)
library(ggpubr)
library(ggplot2)
library(patchwork)
library(ggbeeswarm)

#Reading the data from my working directory using the qualtRics 'read_survey' function - Notably, this function removes the text in rows 2 and 3 (not part of the data)
#This function also sets all relevant columns to 'numeric' rather than 'character', which allows us to do descriptive calculations, mutate new variables, and plot data
mydata=read_survey("Study_1_data.csv")

# Checking the types of variable we have (e.g., numeric, string, character etc.) **Note that relevant columns for calulations are 'numeric'
sapply(mydata, class)

# CONVERT mydata to a data.frame - the qualtRics package Formats the data to a tibble rather than a data frame - converting mydata into a data.frame fixes the rounding issue in my numeric calculations 
mydata<- as.data.frame(mydata)
```

## 1. Filtering Data (Exp 1) 
```{r}

#Count how many times the survey was opened i.e. the number of observations (anyone with progress >= 1%)   [371] 
mydata %>% count(Progress>=1) #371

#Count how many particpants CONSENTED to take part (this is BEFORE any exclusions for non-completion / non-serious responding) [363]
#371 rows in data frame, but only 363 clicked the consent button 
mydata %>% count(Consent==1) #363

#Renaming variables "SC0" to "recall_score" and "FL_10_DO" to "condition"
mydata <- mydata %>% rename(Recall_score = SC0, Condition = FL_10_DO)

#UNPLANNED EXCLUSION: Some participants completed the study twice, thus there are duplicated IDs (identified through the Profilic_PID variable) that must be filtered out
mydata %>% count(duplicated(Prolific_PID)) #count duplicates (TRUE = 59, FALSE = 312)
mydata <- mydata[!duplicated(mydata$Prolific_PID), ] #remove duplicate rows from mydata - this function removes the second (duplicate) response  
mydata %>% count(Progress>=1) #Ensure that the no. of observations are now 312 (59 were removed)

#PLANNED EXCLUSIONS:
# Applying exclusion criteria: participants who finished the study (Finished==1), declared that they answered seriously (seriousness_check==1) AND scored 4 or above on recall
# NOTE: Filtering for 'Finished' excludes those who didn't consent automatically
# THEN creating a subset of relevant variables 

mydata <- mydata %>% 
    filter(
      Finished == 1,
      Serious_check == 1,
      Recall_score >= 4) %>% 
    select(
      Finished,
      `Duration (in seconds)`,
      Gender,
      Age,
      Serious_check, 
      Recall_score,
      Condition,
      contradiction_1:advancement)
  
#Count how many participants remain after exclusions (final sample size = 294)
mydata %>% summarise(n())
Total_n <- mydata %>% summarise(n())

#Export the data to a .csv
write_csv(mydata, "MyDataSubset.csv")
```

## 2. Descriptive stats > Calculating demographics (Exp 1)

```{r}
#AGE: Calculating the mean, SD, and range
mydata %>% summarise(mean(Age), sd(Age), range(Age)) # M = 34.29, SD = 12.67, Range = 18-69

#GENDER: No. of males(Value: '1') and females('2'), Other('3') and Prefer not to say('4'):
mydata %>% count(Gender) #male = 126, female = 168, other = 0, prefer not = 0
```

## 3. Descriptive stats > Descriptive ggplots (Exp 1)

```{r}
##For contradiction plot, must create a NEW variable: sum of the six contradiction ratings
mydata <- mydata %>%
  rowwise() %>%
  mutate(contradiction = sum(contradiction_1, contradiction_2, contradiction_3, contradiction_4, contradiction_5, contradiction_6))

##For all plots
#Separate the data in Condition into 4 columns to separate levels of each IV  ("Block_1_Generic_Conflict", "Block_2_Generic_Consistent", "Block_3_Qualified_Conflict" and "Block_4_Qualified_Consistent")
mydata <- separate(mydata, Condition, c("block", "number", "Format", "Conflict"))

#Set relevant IV columns ("Format" and "Conflict" as factors) 
mydata <- mydata %>%
  mutate(Format=as.factor(Format)) %>%
  mutate(Conflict=as.factor(Conflict))

sapply(mydata, class) #to check

#Export the FINAL data to a .csv
write_csv(mydata, "MyDataTidiedSubset.csv")

##Violin ggplots

#Contradiction plot
contradiction_violinplot <- ggplot(mydata, aes(x = Conflict, y = contradiction, fill = Conflict)) + #fill = colour grouping based on Conflict type
  geom_violin() +   #creating violin plot
  facet_wrap(vars(Format), strip.position = "bottom")+  #dividing plots by format, and changing facet titles to be at the bottom rather than top
  stat_summary(      #adding crossbars to indicate mean of contradiction scores as well as 95% confidence intervals
    mapping = NULL,
    data = NULL,
    geom = "crossbar",
    fun.data = "mean_ci",   #adding 95% confidence intervals
    fill = "white",         #changing colour
    alpha = .7)+            #changing transparency of fill
  geom_beeswarm(cex = 0.2)+             #adding dotpoints to violin plot. cex = scaling for adjusting point spacing
  ggtitle(label = "Contradiction")+     #adding title
  scale_y_continuous(        
    name = "Perceived Contradiction",   #adding y-axis title
    limits = c(0,30))+                 #setting scale from 0 to 30
  scale_x_discrete(name = NULL)+        #removing x-axis title
  theme(plot.title = element_text(hjust = 0.5)) +   #centering the title
  theme(legend.position = 'none') +    #removing legend
  scale_fill_manual(values=c("slategray2", "lightpink1")) #manually changing the fill colours from default colour grouping based on conflict to our desired colours
print(contradiction_violinplot)

#Advancement plot
advancement_violinplot <- ggplot(mydata, aes(x = Conflict, y = advancement, fill = Conflict)) +
  geom_violin() + 
  facet_wrap(vars(Format), strip.position = "bottom")+
  stat_summary(
    mapping = NULL,
    data = NULL,
    geom = "crossbar",
    fun.data = "mean_ci",
    fill = "white",
    alpha = .7)+
  geom_beeswarm(cex = 0.2)+
  ggtitle(label = "Advancement")+
  scale_y_continuous(name = "Perceived Scientific Advancement")+
  scale_x_discrete(name = NULL)+
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(legend.position = 'none') +
  scale_fill_manual(values=c("slategray2", "lightpink1"))
print(advancement_violinplot)

#Confusion plot
confusion_violinplot <- ggplot(mydata, aes(x = Conflict, y = confusion, fill = Conflict)) +
  geom_violin() + 
  facet_wrap(vars(Format), strip.position = "bottom")+
  stat_summary(
    mapping = NULL,
    data = NULL,
    geom = "crossbar",
    fun.data = "mean_ci",
    fill = "white",
    alpha = .7)+
  geom_beeswarm(cex = 0.2)+
  ggtitle(label = "Confusion") +
  scale_y_continuous(name = "Perceived Confusion") +
  scale_x_discrete(name = NULL) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(legend.position = 'none') +
  scale_fill_manual(values=c("slategray2", "lightpink1"))
print(confusion_violinplot)

# Combine plots using the package patchwork()
combinedplots1 <- contradiction_violinplot + advancement_violinplot + confusion_violinplot + plot_layout(ncol = 2)
print(combinedplots1)

```

## 4. Descriptive stats > Pre-registered analysis of group means (Exp 1)

```{r}
##Conflicting vs non. conflicting group means (pre-registered analysis)

#Perceived Contradiction: Participants exposed to conflicting headlines perceived greater contradiction between the six headline pairs (M = 25.3) than those exposed to non-conflicting headlines (M = 13.4)
contradiction_means <- mydata %>%       # Specify data frame
  group_by(Conflict) %>%                # Specify group indicator
  summarise_at(vars(contradiction),     # Specify column
               list(name = mean))       # Specify function
print(contradiction_means)

#Advancement: The mean response of those exposed to non-conflicting headlines (0.007) was greater than the mean response of those exposed to conflicting headlines (-0.25)
advancement_means <- mydata %>%         # Specify data frame
  group_by(Conflict) %>%                # Specify group indicator
  summarise_at(vars(advancement),       # Specify column
               list(name = mean))       # Specify function
print(advancement_means)

#Confusion: Participants exposed to conflicting headlines indicated greater agreement that ‘the headlines create confusion about how to be healthy’ than those exposed to non-conflicting headlines (4.52 vs 3.65 on a 5-point scale)
confusion_means <- mydata %>%           # Specify data frame
  group_by(Conflict) %>%                # Specify group indicator
  summarise_at(vars(confusion),         # Specify column
               list(name = mean))       # Specify function
print(confusion_means)
```

## 5. Descriptive stats > Descriptive Historgram (Exp 1)
```{r}
# The following histogram plots how many people selected  -1 / 0 / +1 on the advancement scale for each of the four conditions

#FIRST adding value labels - using the ordered() function for ordinal data.
advancementvalue <- ordered(mydata$advancement,
        levels = c(-1, 0, 1),
        labels = c("Less", "Same", "More")) #labeling the levels of advancement

advancement_histogram <- ggplot(mydata) + geom_bar(
  aes(
    x=advancementvalue, 
    group = Conflict:Format,    
    fill = Conflict:Format),
  position = "dodge")+     #plotting side by side
  scale_x_discrete(name = "Advancement")+
  scale_y_continuous(name = "Number of Participants")+
  scale_fill_grey(name = "Condition", 
                  labels = c("Conflicting/Generic", 
                             "Conflicting/Qualified",
                             "Non-conflicting/Generic",
                             "Non-conflicting/Qualified"))
print(advancement_histogram)
```

# Experiment 2

```{r}
#Reading the data from my working directory using the qualtRics 'read_survey' function - Notably, this function removes the text in rows 2 and 3 (not part of the data)
#This function also sets all relevant columns to 'numeric' rather than 'character', which allows us to do descriptive calculations, mutate new variables, and plot data
mydata2=read_survey("Study_2_data.csv")

# Checking the types of variable we have (e.g., numeric, string, character etc.) **Note that relevant columns for calculations are 'numeric'
sapply(mydata2, class)

# CONVERT mydata to a data.frame - the qualtRics package Formats the data to a tibble rather than a data frame - converting mydata into a data.frame fixes the rounding issue in my numeric calculations 
mydata2<- as.data.frame(mydata2)

```

## 1. Filtering Data (Exp 2) 

```{r}
#Count how many times the survey was opened i.e. the number of observations (anyone with progress >= 1%) [412] 
mydata2 %>% count(Progress>=1) #412

#Count how many particpants CONSENTED to take part (this is BEFORE any exclusions for non-completion / non-serious responding) [412]
mydata2 %>% count(Consent==1) #412 (ALL were consenting)

#Renaming variables "SC0" to "Recall_score" and "FL_10_DO" to "Condition"
mydata2 <- mydata2 %>% rename(Recall_score = SC0, Condition = FL_12_DO)

#PLANNED EXCLUSIONS:
# Applying exclusion criteria: creating a subset of participants who finished the study (Finished==1), declared that they answered seriously (seriousness_check==1) AND scored 4 or above on recall
# THEN creating a subset of relevant variables 

mydata2 <- mydata2 %>% 
  filter(
    Finished == 1,
    Serious_check == 1,
    Recall_score >= 4) %>% 
  select(
    Finished,
    `Duration (in seconds)`,
    Gender,
    Age,
    Serious_check, 
    Recall_score,
    Condition,
    NC_1:Development_sci_know_6)

#Count how many participants remain after exclusions (final sample size = 400)
mydata2 %>% summarise(n())
Total_n2 <- mydata2 %>% summarise(n())

#Export the subset of data to a .csv
write_csv(mydata2, "MyDataSubset2.csv")

```

## 2. Descriptive stats > Calculating demographics (Exp 2)

```{r}
#AGE: Calculating the mean, SD, and range
mydata2 %>% summarise(mean(Age), sd(Age), range(Age)) # M = 33.5, SD = 12, Range = 18-73

#GENDER: Counting the no. of males(Value: '1') and females('2'), Other('3') and Prefer not to say('4'):
mydata2 %>% count(Gender) #male = 150, female = 248, other = 2, prefer not = 0
```

## 3. Descriptive stats > Descriptive ggplots (Exp 2)

```{r}
##For all plots
#Separate the data in Condition into 4 columns to separate levels of each IV  ("Block_1_Generic_Conflict"...)
mydata2 <- separate(mydata2, Condition, c("block", "number", "Format", "Conflict"))

#set these new IV columns as factors 
mydata2 <- mydata2 %>%
  mutate(Format=as.factor(Format)) %>%
  mutate(Conflict=as.factor(Conflict)) 

sapply(mydata2, class) #to check

#calculate the average for each scale -- library("dplyr")
#nutritional confusion mean
mydata2 <- mydata2 %>%
  rowwise() %>%
  mutate(confusion = (NC_1 + NC_2 + NC_3 + NC_4 + NC_5 + NC_6)/6)

#nutritional backlash mean
mydata2 <- mydata2 %>%
  rowwise() %>%
  mutate(backlash = (NBS_1 + NBS_2 + NBS_3 + NBS_4 + NBS_5 + NBS_6)/6)

#Mistrust of expertise mean
mydata2 <- mydata2 %>%
  rowwise() %>%
  mutate(mistrust = (Mistrust_expertise_1 + Mistrust_expertise_2 + Mistrust_expertise_3)/3)

#Confidence in scientific community = single column ('GSS')

#Certainty of knowledge mean
mydata2 <- mydata2 %>%
  rowwise() %>%
  mutate(certainty = (Certainty_sci_know_1 + Certainty_sci_know_2 + Certainty_sci_know_3 + Certainty_sci_know_4 + Certainty_sci_know_5 + Certainty_sci_know_6)/6)

#Development of knowledge mean
mydata2 <- mydata2 %>%
  rowwise() %>%
  mutate(development = (Development_sci_know_1 + Development_sci_know_2 + Development_sci_know_3 + Development_sci_know_4 + Development_sci_know_5 + Development_sci_know_6)/6)

#Export the FINAL data to a .csv
write_csv(mydata2, "MyDataFinalSubset2.csv")

##Violin ggplots

#Nutritional Confusion plot
nutritionalconfusion_violinplot <- ggplot(mydata2, aes(x = Conflict, y = confusion, fill = Conflict)) +      #fill = colour grouping based on Conflict type
  geom_violin() + #creating violin plot
  facet_wrap(vars(Format), strip.position = "bottom")+  #dividing plots by format, and changing facet titles to be at the bottom rather than top
  stat_summary(   #adding crossbars to indicate mean of contradiction scores as well as 95% confidence intervals
    mapping = NULL,
    data = NULL,
    geom = "crossbar",
    fun.data = "mean_ci",   #adding 95% confidence intervals
    fill = "white",         #changing colour
    alpha = .7)+            #changing transparency of fill
  geom_beeswarm(cex = 0.2)+     #adding dotpoints to violin plot. cex = scaling for adjusting point spacing
  ggtitle(label = "Nutritional Confusion")+    #adding title
  scale_y_continuous(                          #adding y-axis title
    name = "Nutritional Confusion")+        
  scale_x_discrete(name = NULL)+               #removing x-axis title
  theme(plot.title = element_text(hjust = 0.5)) +    #centering the title
  theme(legend.position = 'none') +                  #removing legend
  scale_fill_manual(values=c("slategray2", "lightpink1"))    #manually changing the fill colours from default colour grouping based on conflict to our desired colours
print(nutritionalconfusion_violinplot)

#Nutritional Backlash plot
nutritionalbacklash_violinplot <- ggplot(mydata2, aes(x = Conflict, y = backlash, fill = Conflict)) +
  geom_violin() + 
  facet_wrap(vars(Format), strip.position = "bottom")+
  stat_summary(
    mapping = NULL,
    data = NULL,
    geom = "crossbar",
    fun.data = "mean_ci",
    fill = "white",
    alpha = .7)+
  geom_beeswarm(cex = 0.2)+
  ggtitle(label = "Nutritional Backlash")+
  scale_y_continuous(
    name = "Nutritional Backlash")+
  scale_x_discrete(name = NULL)+
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(legend.position = 'none') + 
  scale_fill_manual(values=c("slategray2", "lightpink1"))
print(nutritionalbacklash_violinplot)

#Mistrust of Expertise plot
mistrust_violinplot <- ggplot(mydata2, aes(x = Conflict, y = mistrust, fill = Conflict)) +
  geom_violin() + 
  facet_wrap(vars(Format), strip.position = "bottom")+
  stat_summary(
    mapping = NULL,
    data = NULL,
    geom = "crossbar",
    fun.data = "mean_ci",
    fill = "white",
    alpha = .7)+
  geom_beeswarm(cex = 0.2)+ 
  ggtitle(label = "Mistrust of Expertise")+
  scale_y_continuous(
    name = "Mistrust of Expertise")+
  scale_x_discrete(name = NULL)+
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(legend.position = 'none') + 
  scale_fill_manual(values=c("slategray2", "lightpink1"))
print(mistrust_violinplot)

#Confidence in Scientific Community plot
confidence_violinplot <- ggplot(mydata2, aes(x = Conflict, y = GSS, fill = Conflict)) +
  geom_violin() + 
  facet_wrap(vars(Format), strip.position = "bottom")+
  stat_summary(
    mapping = NULL,
    data = NULL,
    geom = "crossbar",
    fun.data = "mean_ci",
    fill = "white",
    alpha = .7)+
  geom_beeswarm(cex = 0.2)+ 
  ggtitle(label = "Confidence in Scientific Community")+
  scale_y_continuous(
    name = "Confidence in Scientific Community")+
  scale_x_discrete(name = NULL)+
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(legend.position = 'none') + 
  scale_fill_manual(values=c("slategray2", "lightpink1"))
print(confidence_violinplot)

#Certainty of Knowledge plot
certainty_violinplot <- ggplot(mydata2, aes(x = Conflict, y = certainty, fill = Conflict)) +
  geom_violin() + 
  facet_wrap(vars(Format), strip.position = "bottom")+
  stat_summary(
    mapping = NULL,
    data = NULL,
    geom = "crossbar",
    fun.data = "mean_ci",
    fill = "white",
    alpha = .7)+
  geom_beeswarm(cex = 0.2)+ 
  ggtitle(label = "Certainty of Knowledge")+
  scale_y_continuous(
    name = "Certainty of Knowledge")+
  scale_x_discrete(name = NULL)+
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(legend.position = 'none') + 
  scale_fill_manual(values=c("slategray2", "lightpink1"))
print(certainty_violinplot)

#Development of Knowledge plot
development_violinplot <- ggplot(mydata2, aes(x = Conflict, y = development, fill = Conflict)) +
  geom_violin() + 
  facet_wrap(vars(Format), strip.position = "bottom")+
  stat_summary(
    mapping = NULL,
    data = NULL,
    geom = "crossbar",
    fun.data = "mean_ci",
    fill = "white",
    alpha = .7)+
  geom_beeswarm(cex = 0.2)+ 
  ggtitle(label = "Development of Knowledge")+
  scale_y_continuous(
    name = "Development of Knowledge", limits = c(1,5))+
  scale_x_discrete(name = NULL)+
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(legend.position = 'none') + 
  scale_fill_manual(values=c("slategray2", "lightpink1"))
print(development_violinplot)

# Combine plots using the package patchwork()
combinedplots2 <- nutritionalconfusion_violinplot + nutritionalbacklash_violinplot + mistrust_violinplot + confidence_violinplot + certainty_violinplot + development_violinplot + plot_layout(ncol = 2)
print(combinedplots2)

```

