---
title: "Verification Report - Experiemnt 1"
author: "Torunn Briers"
date: "03/07/2021"
output:
  html_document:
    theme: "cosmo"
    toc: true
    toc_float: true
---
<style type="text/css">
body {
  font-size: 11pt;
}
h1 {
  font-size: 18pt;
}
h2 {
  font-size: 15pt;
}
</style>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Set up and tidy data

## Loading packages 
```{r, results='hide', message=FALSE}
library(tidyverse)
library(ggplot2)
library(janitor)
library(ggeasy)
library(ggbeeswarm)
library(kableExtra)
library(devtools)
library(psych)
library(qualtRics)
```

## Reading the data
```{r, results='hide', message=FALSE}
Exp_1_data <- read_csv(file= "./data/Study_1_data.csv") # Named my data Exp_1_data (Experiment 1 data)
```

## Remove lines 2 and 3 
```{r, results='hide', message=FALSE}
# Exp_1_data <- Exp_1_data %>% slice(-1:-2) 

Exp_1_data = read_survey("./data/Study_1_data.csv")
```

## Make data into a data fram 
```{r, results='hide', message=FALSE}
Exp_1_data <- as.data.frame(Exp_1_data) 
```

## Rename incomprehensible variable names 
```{r, results='hide', message=FALSE}
Exp_1_data <- Exp_1_data %>% 
  rename(recall_score = SC0, condition = FL_10_DO) 
```

## Unplanned and planned exclusions 
```{r, results='hide', message=FALSE}
# Unplanned exclusions  -------------------------------------------------

Exp_1_data <- Exp_1_data %>% 
  distinct(Prolific_PID, .keep_all = TRUE) 

# Planned exclusions  -----------------------------------------------------

Exp_1_data <- Exp_1_data %>%
  filter(Finished == 1, Serious_check == 1, recall_score >= 4) 
```

## Changing and creating variables

### Separating the IVs
```{r, results='hide', message=FALSE}

Exp_1_data <- Exp_1_data %>% 
  separate(col = condition, into = c("block", "number", "Format", "Conflict"))
```

### changing IVs from characters to factors 
```{r, results='hide', message=FALSE}
Exp_1_data$Format <- as.factor(Exp_1_data$Format)

Exp_1_data$Conflict <- as.factor(Exp_1_data$Conflict)
```

### renaming factors of 'Conflict'
```{r,results='hide', message=FALSE}
Exp_1_data$Conflict <- recode_factor(Exp_1_data$Conflict,
                                      Conflict = "Conf.",
                                      Consistent = "Non-Conf.")
```

### changing DVs from characters to numeric 
```{r, results='hide', message=FALSE}

Exp_1_data$advancement <- as.numeric(Exp_1_data$advancement)

Exp_1_data$confusion <- as.numeric(Exp_1_data$confusion) 
```

### Change from Character to Numeric for all contradiction variables
```{r, results='hide', message=FALSE}
Exp_1_data$contradiction_1 <- as.numeric(Exp_1_data$contradiction_1)
Exp_1_data$contradiction_2 <- as.numeric(Exp_1_data$contradiction_2)
Exp_1_data$contradiction_3 <- as.numeric(Exp_1_data$contradiction_3)
Exp_1_data$contradiction_4 <- as.numeric(Exp_1_data$contradiction_4)
Exp_1_data$contradiction_5 <- as.numeric(Exp_1_data$contradiction_5)
Exp_1_data$contradiction_6 <- as.numeric(Exp_1_data$contradiction_6)
```

### Create new variable called "Contradiction" that is the sum of all 6 contradiction ratings
```{r, results='hide', message=FALSE}
Exp_1_data <- Exp_1_data %>% 
  rowwise() %>% 
  mutate(
    Contradiction = sum(
      contradiction_1, contradiction_2, contradiction_3, contradiction_4, contradiction_5, contradiction_6)) %>% 
  as.data.frame() # changes data back into a data frame 
```

# Demographic statistics

## Check no. of participants 

**No. of participants: 294** 
```{r, results='hide', message=FALSE}
count(Exp_1_data)
```

## Number of male and female partipants 

- By looking at the survey (provided in the OSF files) I could see that males were coded as 1 and females as 2 
- **No. of male participants: 126**
- **No. of female participants: 168** 

Before counting gender I change the names of the Gender variables to 'male' and 'female' so that the following table is more clear.
``` {r}
Exp_1_data$Gender <- recode_factor(Exp_1_data$Gender,
                                   '1' = "Male",
                                   '2' = "Female", 
                                   '3' = "Other",
                                   '4' = "Prefer not to say") 
```

``` {r}
Exp_1_data %>% group_by(Gender) %>% count(Gender) %>% kbl %>% kable_styling()
```

## Age demographics 

- **Mean Age: 34.29, SD: 12.97, Age Range: 18-69**
- The mean, standard deviation and range of the age of participants is calculated using the `summarise()` function. I installed and loaded the "kableExtra" package to use the functions `kbl` and `kable_styling()` to put my results in a nice table.

```{r}
Exp_1_data %>% summarise(mean_age = mean(Age),
                         SD = sd(Age), 
                         min_age = min(Age), 
                         max_age = max(Age)
                         ) %>% kbl %>% kable_styling()
```

# Descriptive stats 

In Experiment 1 there are three dependent variables - 'Perceived Contradiction', 'Confusion' and 'Scientific Advancement'. 

## Perceived Contradiction

'Perceived Contradiction' was measured using a 5-point scale where the participant indicated the degree to which they thought each of the 6 pairs of headlines contradicted one another. The overall score was the sum of the six items (6 - 30), with a higher score indicating that a participant perceived a greater degree of contradiction. 

The study found that participants exposed to conflicting headlines had a mean rating of 25.3 and participants exposed to non-conflicting headlines had a mean rating of 13.4.

To calculate these values we create a new object 'contradiction_means' and use the assignment operator to first select the data to be used (Exp_1_data) and then pipe it through the `group_by()` function which selects the variable 'Conflict'. We then pipe it through the `summarise()` function which select the mean of the variable 'Contradiction'. 

```{r}
contradiction_means <- Exp_1_data %>% 
  group_by(Conflict) %>% 
  summarise(mean= mean(Contradiction, na.rm = TRUE)) 

contradiction_means
```
## Confusion

"Confusion' was measured using a 5-point scale where the participant indicated the degree to which they thought the headlines were confusing. 

The study found that participants exposed to conflicting headlines had a mean rating of 4.52 and participants exposed to non-conflicting headlines had a mean rating of 3.65. 

These values were calculated in the same was as 'Perceived Contradiction', only `summarise()` was used to give the mean of the variable 'confusion'. 

```{r}
confusion_means <- Exp_1_data %>% 
  group_by(Conflict) %>% 
  summarise(mean= mean(confusion, na.rm = TRUE))

confusion_means
```

## Scientific Advancement

'Scientific Advancement' was measured by asking the participants to indicate if they felt they knew more, less or the same as they did before reading the headlines. This was coded as -1 for 'less', 0 for 'same' and 1 for 'more.

The study found that participants exposed to non-conflicting headlines had a mean score of 0.007 and participants exposed to conflicting headlines had a mean score of -0.25. 

Again these values were calculated in the same way as the previous two variable but with  `summarise()` used to give the mean of the variable 'advancement'. 

```{r}
advancement_means <- Exp_1_data %>% 
  group_by(Conflict) %>% 
  summarise(mean= mean(advancement, na.rm = TRUE))

advancement_means
```

# Reproducing Firgure 1

## Creating the contradiction plot

```{r, results='hide', message=FALSE}
contradiction_plot <- ggplot(Exp_1_data, aes(x= Conflict, y= Contradiction, fill = Conflict)) + 
  geom_violin() + 
  geom_beeswarm(cex = 0.2) + 
  theme(legend.position = "none") +
  geom_crossbar(mapping = NULL, data = NULL, stat= "summary", fun.y = "mean_ci", fill = "white", alpha = 0.7, width = 0.8) +  
  facet_wrap(vars(Format), strip.position = "bottom") + 
  ggtitle(label= "Contradiction") + 
  theme(plot.title = element_text(hjust= 0.5)) + 
  theme_minimal() +
  scale_y_continuous(name = "Perceived Contradiction", limits = c(0,30)) + 
  scale_fill_manual(values=c("slategray2", "lightpink1")) +
  easy_remove_legend()

print(contradiction_plot)
```


## Creating the Advancement plot 
```{r, results='hide', message=FALSE}

advancement_plot <- ggplot(Exp_1_data, aes(x= Conflict, y= advancement, fill = Conflict)) +  
  geom_violin() + 
  facet_wrap(vars(Format), strip.position = "bottom") + 
  ggtitle(label= "Advancement") + 
  scale_y_continuous(name= "Perceived Scientific Advancement", breaks = seq(from = -1, to = 1)) + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  geom_beeswarm(cex = 0.2) + 
  theme(legend.position = "none") + 
   theme_minimal() +
  geom_crossbar(stat="summary", fun.y= "mean_ci", fill = "white", alpha = 0.7, width = 0.8) + 
  scale_fill_manual(values=c("slategray2", "lightpink1")) +
  easy_remove_legend()

print(advancement_plot)
```

## Creating the Confusion plot 
```{r, results='hide', message=FALSE}

confusion_plot <- ggplot(Exp_1_data, aes(x= Conflict, y = confusion, fill = Conflict)) +
  geom_violin() + 
  facet_wrap(vars(Format), strip.position= "bottom") + 
  ggtitle(label= "Confusion") + 
  scale_y_continuous(name= "Perceived Confusion", limits= c(1,5)) +
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(legend.position = "none") +
  theme_minimal() +
  geom_beeswarm(cex = 0.2) +
  geom_crossbar(stat="summary", fun.y= "mean_ci", fill = "white", alpha = 0.7, width = 0.6)  +
  scale_fill_manual(values=c("slategray2", "lightpink1"))+
  easy_remove_legend()

print(confusion_plot)
```

# Reproducing Figure. 2 

Figure. 2 is a histogram "displaying the number of participants in each condition who felt the body of research reported in the headlines resulted in us knowing more than before, less than before or the same as before". In the data, -1 was recorded if the participant reported feeling less than before, 0 if they reported knowing the same as before and 1 if they reported knowing more than before. 

Therefore, the first step in creating this plot was to label these three values as "less", "same" and "more". To do this we created a new object 'advancement_levels' and used the function `factor()` to specify the levels of the factor (-1, 0, 1) and then label them less", "same" and "more" respectively.

```{r, results='hide', message=FALSE}
advancement_levels <- factor(Exp_1_data$advancement,
                                   levels = c(-1, 0, 1),
                                   labels = c("Less", "Same", "More")) 

```

To create the histogram we first create a new object 'advancement_histogram' and use the assignment operator `<-` to assign variables to this object. We use the function `ggplot()` establish the object as a plot and to select the necessary input data frame - 'Exp_1_data'. We then use `+` to add other components to the plot. First we use `geom_bar()` (from the ggplot2 package) to make the plot a bar chart. `geom_bar` is then given the argument `aes` to construct 'aesthetic mappings' for the plot - basically deciding which variable will be included in the plot and how they will be presented. The x axis is set to be the 'advancement_levels' (less, same, more) created previously. `group` is then used to divide these three levels of advancement into the four experiemntal conditions ("Conflicting/Generic", "Conflicting/Qualified", "Non-conflicting/Generic" and "Non-conflicting/Qualified"). `fill` is used to colour each bar based on the condition it represents and `position` is set as "dodge" which arranges the groups (experimental condition) of each level side-by-side instead of stacked on top of one another - in other words, each level has 4 bars (one for each condition) rather than one big bar). 

The function `scale_x_discrete` is used to label the x axis and ` scale_y_continuous` is used to label the y axis. We use "scale_*_grey" to create a grey colour gradient (and corresponding ledgend). By inserting 'fill' (`scale_fill_grey`) it is applied to what we have previously specified for `fill` - the experimental condition. We then give this function the argument `name` which is used to give the legend the label "Condition" and then the argument `labels` to specify what condition each colour represents.

Finally, `print` is used to make the plot visible to us. 
```{r}
#making the histogram 

advancement_histogram<-ggplot(Exp_1_data) +
  geom_bar(aes(x=advancement_levels, 
               group=Conflict:Format,                     
               fill = Conflict:Format),                  
           position = "dodge") + 
  scale_x_discrete(name = "Advancement")+ 
  scale_y_continuous(name = "Number of Participants") +
  scale_fill_grey(name = "Condition",                     
                  labels = c("Conflicting/Generic",       
                             "Conflicting/Qualified", 
                             "Non-conflicting/Generic", 
                             "Non-conflicting/Qualified")) 


print(advancement_histogram) #print 
```

