---
title: "animal rescues"
author: "Jen Richmond"
date: "30/06/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load packages
<<<<<<< HEAD

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(janitor)
library(ggeasy)
```

# read data

```{r message=FALSE, warning=FALSE}
animal_rescues <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-06-29/animal_rescues.csv')

```

# clean data

```{r}
by_animal <- animal_rescues %>%
  tabyl(animal_group_parent) 

```


```{r}
by_animal <- by_animal %>%
  select(-3) %>%
  rename(animal = animal_group_parent, number_of_rescues = n)
=======
Use janitor for cleaning - cleans name to remove spaces and replace with _, make all lowercase.
Use ggeasy to allow easy formatting of the plots. 
```{r message=FALSE, warning=FALSE}
library(tidyverse) 
library(janitor) #for cleaning - cleans name to remove spaces and replace with _, make all lowercase
library(ggeasy) #to allow easy formatting of the plots
```

# read data
Reading CSV file from link and creating the new data 'animal_rescues'
```{r message=FALSE, warning=FALSE}
animal_rescues <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2021/2021-06-29/animal_rescues.csv') #reading CSV file from link and creating the new data 'animal_rescues'
```

# clean data
Creating new data 'by_animal', count variable 'animal_group_parent' to give total number and % of each animal group.
```{r}
by_animal <- animal_rescues %>%
  tabyl(animal_group_parent) #creating new data 'by_animal', count variable 'animal_group_parent' to give total number and % of each animal group

```

We use select function with (-3) to remove third column - '% of total animals rescued.
Use rename for renaming variables - in the format 'new name = old name'
```{r}
by_animal <- by_animal %>%
  select(-3) %>% #remove third column '%' 
  rename(animal = animal_group_parent, number_of_rescues = n) #renaming variables - 'new name = old name'
>>>>>>> 74850d7ded8d0fadb716137c436e832043d12aa1

```

```{r}
<<<<<<< HEAD
top5 <- by_animal %>%
  arrange(-number_of_rescues) %>%
  slice(1:5)
```

# visualise data
=======
top5 <- by_animal %>% #create new data 'top5' from 'by_animal'
  arrange(-number_of_rescues) %>% #arrange number of rescues in descending order (highest to lowest)
  slice(1:5) #select rows 1 to 5
```

# visualise data
Plot using 'top 5' data using function ggplot. Aesthetic argument is used to choose the variables for x- and y-axes. The x-axis is type of animal, y-axis total number of rescues. Use geom_col to plot it as a column graph.
>>>>>>> 74850d7ded8d0fadb716137c436e832043d12aa1

```{r}
top5 %>%
  ggplot(aes(x = animal, y = number_of_rescues)) +
  geom_col()
  
```

<<<<<<< HEAD
=======
Plot using 'top 5' data using function ggplot. Reordering graph above in descending order of number of rescues. Use coord_flip function so that instead of vertical, we view it as horizontal.

>>>>>>> 74850d7ded8d0fadb716137c436e832043d12aa1
```{r}
top5 %>%
  ggplot(aes(x = reorder(animal, number_of_rescues), y = number_of_rescues, fill = animal)) +
  geom_col() +
  coord_flip()
```

<<<<<<< HEAD
=======
Formatting - cleaning us the axes titles. Labs function used to change title of axes.
Remove legend using. 
>>>>>>> 74850d7ded8d0fadb716137c436e832043d12aa1
```{r}
top5 %>%
  ggplot(aes(x = reorder(animal, number_of_rescues), y = number_of_rescues, fill = animal)) +
  geom_col() +
  coord_flip() +
  theme_classic() +
  labs(x = "Animal", y = "Number of rescues") +
  easy_remove_legend()
```

